---
title: "Peira Evaluation of iStar-RL"
author: "Markdown prepared by Sotirios Liaskos"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, eval = FALSE)
setwd("../../Analyzer")
source("PackageLoad.R")
source("Analyzer.R")
setwd("../Generator")
source("Generator.R")
source("Library.R")
setwd("../Projects/iRL")
```

# Preliminary: Load Libraries and Set Paths

```{r eval=TRUE}
lan = "iRL"
lan_long = "iStar-RL"
configID = "config"

dPath = "Data/config - 25-02-26 12-58-16/"
mdPath = "Data/config - 25-02-26 12-58-16/"
paperPath = "Paper/"

confData = getConfigData(mdPath,configID)

# Load data sets from configuration directory
concepts_df = confData$concepts_df
lang_df = confData$lang_df
config = confData$config
cases_df = confData$cases_df
items_df = confData$items_df


printTEXData = FALSE
printIMGData = FALSE

```




# Create dataframes

```{r eval=TRUE}

# Observational Data
ds1 = getObservationalData(lan,dPath,mdPath)
# Self reported Data
ds2 = getAttitudinalData(lan,dPath,mdPath)
# Demographic Data
dse = getDemographicData(lan,dPath,mdPath)

participants_clean = nrow(unique(ds1$participant))
participants_unclean = 0

totalInvited = participants_clean + participants_unclean 

if (printTEXData) {
  sink(file = paste0(paperPath,lan,"-totalInvited.tex"))
  cat(reportNumber(totalInvited))
  sink(file = NULL)
}

if (printTEXData) {
  sink(file = paste0(paperPath,lan,"-Excluded.tex"))
  cat(reportNumber(participants_unclean))
  sink(file = NULL)
}

```


# Instrument Statistics

```{r eval = TRUE}
#
#
# * * I N S T R U M E N T    S T A T I S T I C S  * * -------------
#
#

concIDLevels = c(getConceptCodeList_Entities(lan,concepts_df),getConceptCodeList_Relationships(lan,concepts_df))
concTable = rbind(getConceptTable_Entities(lan,concepts_df),getConceptTable_Relationships(lan,concepts_df))
concTable$conceptID = factor(concTable$conceptID)

instru.stats = 
ds1 %>% filter(auth == psy_option,description == "therm") %>% group_by(participant,auth) %>% summarise(occs = n()) %>% 
  group_by(auth) %>% summarise(n2 =mean(occs))  %>%
  mutate (auth = factor(auth, levels = concIDLevels)) %>% arrange(auth) %>% left_join(concTable, by = c("auth" = "conceptID")) %>% select(conceptDescr, n2) %>% rename (Concept = conceptDescr, " # Elements" = n2)


kable(instru.stats)

if (printTEXData) {
  sink(file = paste0(paperPath,lan,"-instrumentStats.tex"))
  print(xtable(instru.stats.1,
               caption = "Number of elements by authoritative designation.",
               label = "tab:auths.case",
               digits= 0))
  sink(file = NULL)
}

```

# Demographics

```{r eval = TRUE}
#
#
# * * D E M O G R A P H I C S  * * -------------
#
#

sexage = rbind(
  dse %>% filter(demo_item_name %in% c("Age","Sex")) %>% mutate(Condition = lan_long)
  ) %>% pivot_wider(id_cols = c(participant,Condition), names_from = demo_item_name,values_from = demo_item_label) %>% 
  group_by(Condition, Sex) %>% summarise(`Average Age` = mean(as.numeric(Age)), Count = n())

kable(sexage %>% ungroup() %>% select(-Condition))
if (printTEXData) {
  sink(file = paste0(paperPath,lan,"-demoTable.tex"))
  print(xtable(sexage %>% ungroup() %>% select(-Condition)
         , caption = "Participants Counts and Ages by Sex."
         , label = "tab:dems"
         , digits = 0
  ))
  sink(file = NULL)
}
```


# Accuracy {.tabset}

## Preliminary - General Stats

```{r eval=TRUE}
#
# * A C C U R A C Y ---------------
#

observations = ds1 %>% select(participant, item, item_full, language, type, psy_option, response) %>% rename("option" = psy_option,"class" = type)
authoritative = ds1 %>% select(item, language, auth) %>% distinct()

acc.pc.out = accuracy.per.concept(observations, authoritative)
acc.data = acc.pc.out$acc.data
acc.pc = acc.pc.out$acc.per.concept
acc.overall = acc.pc.out$acc.per.language %>% mutate(language = getLangName(lan))

kable(acc.overall,"simple")
kable(acc.pc %>% mutate(language = getLangName(lan)) %>% select(-language),"simple")

if (printTEXData) {
  sink(file = paste0(paperPath,lan,"-acc-prec.tex"))
  cat(paste0(round(acc.overall %>% filter(language == getLangName(lan)) %>% pull(precision),1),"\\%"))
  sink(file = NULL)

  sink(file = paste0(paperPath,lan,"-acc-recl.tex"))
  cat(paste0(round(acc.overall %>% filter(language == getLangName(lan)) %>% pull(recall),1),"\\%"))
  sink(file = NULL)
}
```


## Per-concept analysis

```{r eval=TRUE}



set.seed(123)

accuracy.ents = accuracyBoot(acc.data,
              conceptStruct = list(iRL = getConceptCodeList_Entities(lan,concepts_df))) %>% mutate (Language = getLangName(lan))

accuracy.rels = accuracyBoot(acc.data,
              conceptStruct = list(iRL = getConceptCodeList_Relationships(lan,concepts_df))) %>% mutate (Language = getLangName(lan))


kable(accuracy.ents %>% select(Concept, Recall, Precision),"simple")
kable(accuracy.rels %>% select(Concept, Recall, Precision),"simple")

areYouSure = FALSE
if (printTEXData & areYouSure) {
  sink(file = paste0(paperPath,lan,"-acc-bootTable-ent.tex"))
  print(xtable(accuracy.ents %>% select(Language, Concept, Recall, Precision),
       caption = "Accuracy measures for entities (\\%). In brackets the 2.5th and 97.5th percentiles of 
       the bootstrapping distribution created by re-sampling with replacement the authoritative and 
       response sets 1000 times and recalculating the measures.",
       label = "tab:boot.acc.entity"))
  sink(file = NULL)
  
  sink(file = paste0(paperPath,lan,"-acc-bootTable-rel.tex"))
  print(xtable(accuracy.rels %>% select(Language, Concept, Recall,Precision),
       caption = "Accuracy measures for relationships (\\%). In brackets the 2.5th and 97.5th percentiles of 
       the bootstrapping distribution created by re-sampling with replacement the authoritative and 
       response sets 1000 times and recalculating the measures.",
       label = "tab:boot.acc.relationship"
  ))
  sink(file = NULL)
}

(euler.Ent = grid.arrange(print_Euler(acc.pc,lan,"actor"),
                          print_Euler(acc.pc,lan,"goal"),
                          print_Euler(acc.pc,lan,"qual"),
                          print_Euler(acc.pc,lan,"qual-pre"),
                          print_Euler(acc.pc,lan,"eff-sat"),
                          print_Euler(acc.pc,lan,"eff-nonsat"),
                          print_Euler(acc.pc,lan,"eff-pre"),
                          print_Euler(acc.pc,lan,"eff-ind"),ncol = 4))

(euler.Rel = grid.arrange(
               print_Euler(acc.pc,lan,"and"),
               print_Euler(acc.pc,lan,"or"),
               print_Euler(acc.pc,lan,"contr"),
               print_Euler(acc.pc,lan,"pre"),
               print_Euler(acc.pc,lan,"wants"),
               print_Euler(acc.pc,lan,"contr-pos"),
               print_Euler(acc.pc,lan,"contr-neg"),
               print_Euler(acc.pc,lan,"eff-link-det"),
               print_Euler(acc.pc,lan,"eff-link-nondet"),
               ncol = 3))

if (printIMGData){
  ggsave(plot = euler.Ent , paste0(paperPath,"img/",lan,"-fig-acc.ent.pdf"), width = 350/2, height = 180/2, units = "mm")
  ggsave(plot = euler.Rel , paste0(paperPath,"img/",lan,"-fig-acc.rel.pdf"), width = 350/2, height = 180/2, units = "mm")
}
```














# Deficit {.tabset}

## Descriptives per item
```{R eval=TRUE}
#
#  Descriptives per item ---------------
#

def.outcome = deficit(observations)
def.item = def.outcome$def.item
def.tab = def.outcome$def.tab
def.parti = def.outcome$def.parti %>% mutate(language = factor(language,levels = c(lan)))

# Goal Models: Entities
def.graph.conc = ggplot(data = def.item %>% filter(class == "entity"),
  aes(x = Deficit)) + geom_histogram(bins = 9,boundary = 0) + bigthema +
geom_density(alpha=.2, fill="#66FF66") + xlim(c(0,1)) + ggtitle(paste0(lan_long,": Entities"))
#

# Goal Models: Relationships
def.graph.rel = ggplot(data = def.item %>% filter(class == "relationship"),
                       aes(x = Deficit)) + geom_histogram(bins = 9,boundary = 0) + bigthema +
  geom_density(alpha=.2, fill="#66FF66") + xlim(c(0,1)) + ggtitle(paste0(lan_long,": Relationships"))
#

if (printIMGData){
  ggsave(plot = arrangeGrob(def.graph.conc,def.graph.rel), 
         paste0(paperPath,"img/", lan,"-fig-def.hist.pdf"), width = 350, height = 180, units = "mm")
}

x = arrangeGrob(def.graph.conc,def.graph.rel)

def.hists = grid.arrange(def.graph.conc + thema,
                         def.graph.rel + thema)


def.tab.prez = def.tab %>% mutate(
  Language = getLangName(lan),
  Class = ifelse(class == "entity","Entities", "Relationships")) %>%
     ungroup() %>% select(Class,max,q95,q90,q75) %>% arrange(Class)

kable(def.tab.prez, digits = 2)

areYouSure = TRUE
if (printTEXData & areYouSure){
  sink(file =  paste0(paperPath,lan,"-def-deftable.tex"), append = FALSE)
  print(xtable(def.tab.prez,caption = "Deficit measures: maximum observed, and 95th, 90th and 75th quantile.",label = "tab:def"),
      include.rownames = F)
  sink(file = NULL)
}
```

## Items with the most deficit

```{r eval = TRUE}
kable(head(def.item %>% ungroup() %>% filter(class == "entity",language == "iRL") %>% select(item_full,Deficit) %>% rename("Item" = "item_full") %>% arrange(-Deficit)))

head(def.item %>% ungroup() %>% filter(class == "relationship",language == "iRL") %>% select(item_full,Deficit) %>% rename("Item" = "item_full")%>% arrange(-Deficit))
```


## Self-reported
```{r eval = TRUE}
likert_labels <- c(
  "-7" = "Strongly Disagree",
  "-6" = "Strongly Disagree",
  "-5" = "Disagree",
  "-4" = "Disagree",
  "-3" = "Somewhat Disagree",
  "-2" = "Somewhat Disagree",
  "-1" = "Neutral",
  "0"  = "Neutral",
  "1"  = "Neutral",
  "2"  = "Somewhat Agree",
  "3"  = "Somewhat Agree",
  "4"  = "Agree",
  "5"  = "Agree",
  "6"  = "Strongly Agree",
  "7"  = "Strongly Agree"
)

likert_labels_tibble <- tibble(response = unique(likert_labels))

self.conc.compl = ds2 %>% filter(psy_item == "entityCompleteness_1") %>% 
  inner_join(def.parti %>% filter(class == "entity")) %>% select(participant,value,Deficit)
self.rels.compl = ds2 %>% filter(psy_item == "relationshipCompleteness_1") %>% 
  inner_join(def.parti %>% filter(class == "relationship")) %>% select(participant,value,Deficit)

self.compl.all = rbind(self.conc.compl %>%  mutate(class = "Entity"),
    self.rels.compl %>% mutate(class = "Relationship")
) %>% mutate(response = dplyr::recode(as.character(value), !!!likert_labels)) 



zeroLabels = rbind(tibble(class = "Entity",response = unique(likert_labels), count = 0),
      tibble(class = "Relationship",response = unique(likert_labels), count = 0)
      )

self.compl.table.count = self.compl.all %>%
  group_by(class, response) %>% 
  summarize(count = n()) %>% 
  bind_rows(zeroLabels) %>% 
  mutate(response = factor(response, levels = unique(likert_labels))) %>% 
  group_by(class, response) %>% 
  summarize(count = sum(count)) %>% 
  pivot_wider(names_from = response,values_from = count)

self.compl.totals = self.compl.all %>%
  group_by(class, response) %>% 
  summarize(count = n()) %>% 
  bind_rows(zeroLabels) %>% summarise(s = sum(count)) %>% 
  pull(s) %>%
  setNames(unique(self.compl.all$class))

self.compl.table.frequency = self.compl.table.count %>% 
  pivot_longer(-class, names_to = "response") %>%
  mutate(value = if_else(class == "Entity", value/self.compl.totals["Entity"], 
                         value/self.compl.totals["Relationship"])) %>%
  mutate(response = factor(response, levels = unique(likert_labels))) %>% 
  pivot_wider(names_from = response, values_from = value) %>%
  ungroup() %>%
  #mutate(across(-class, ~ . * 100)) %>%  # Convert to percentage
  mutate(across(-class, ~ paste0(round(. * 100, 1), "%")))
  

# Generate kable for the table
self.compl.table.frequency %>%
    kable(digits = 1, caption = "Self-reported decific by concept class","simple") 


areYouSure = TRUE
if (printTEXData & areYouSure){
  sink(file =  paste0(paperPath,lan,"-def-self-reported.tex"), append = FALSE)
  self.compl.table.frequency %>%
    kable(format = "latex", digits = 1, caption = "Self-reported decific by concept class",label = "tab:def-self") 
  sink(file = NULL)
}



likert_def_df = tibble(Entities =  self.compl.all %>% select(class,response) %>% filter(class == "Entity") %>% pull(response),
Relationships = self.compl.all %>% select(class,response) %>% filter(class == "Relationship") %>% pull(response))

likert_def_df$Entities = factor(likert_def_df$Entities,levels = unique(likert_labels))
likert_def_df$Relationships = factor(likert_def_df$Relationships,levels = unique(likert_labels))

likert_def_df = likert_def_df %>% mutate(across(everything(), factor, levels = unique(likert_labels)))

(likert_def_fig = plot(likert(data.frame(likert_def_df),nlevels = 7)))

if (printIMGData){
  ggsave(plot = likert_def_fig, 
         paste0(paperPath,"img/", lan,"-fig-def.likert.pdf"), width = 200, height = 90, units = "mm")
}

```

## Observed vs. self-reported

```{r eval = TRUE}


(def.self.corr = cor.test(self.compl.all[,"value"]$value,
         self.compl.all[,"Deficit"]$Deficit,
         method = "kendall",exact = FALSE,alternative = "less"))

if (printTEXData) {
  sink(file = paste0(paperPath,lan,"-def.self.corr.tex"))
  cat(reportKendalCor(def.self.corr,alpha = expAlphaLevel/(selfExps)))
  sink(file = NULL)
}

def.self.corr.plot = ggplot(self.compl.all,aes(x=value, y = Deficit)) + 
  geom_point() + geom_smooth(method='lm', formula= y~x) +
  xlab("Self-Reported Completeness") + ylab("Observed Deficit") + bigthema
  
if (printIMGData) {
   ggsave(plot = def.self.corr.plot, paste0(paperPath,"img",lan,"-fig-self.def.pdf"), 
          width = 350, height = 180, units = "mm")
}
``` 


# Excess {.tabset}

## Descriptives

```{r eval=TRUE}
exc.outcome = excess(observations)
exc.data = exc.outcome$exc.data
exc.descr = exc.outcome$exc.descr
exc.pp = exc.outcome$exc.per.participant

exc.table = exc.descr %>% ungroup() %>% #mutate(Language = getLangName(lan)) %>%
        select(-language) %>% rename_with(str_to_title) # %>% relocate(Language,.before = Class),

kable(exc.table,
      digits = 2,"simple")
      
      
areYouSure = TRUE
if (printTEXData & areYouSure){
  sink(file = paste0(paperPath,lan,"-exc.table.tex"))
  print(xtable(exc.table,caption = "Excess measures: maximum observed, and 95th, and 90th quantile.",label = "tab:exc"),
      include.rownames = F)
  sink(file = NULL)
}

```

## Self-reported excess
```{r eval=TRUE}
exc.ent.countarray = 1:length(getConceptList_Entities(lan))
exc.rel.countarray = 1:length(getConceptList_Relationships(lan))

exc.sr.ent = ds2 %>% filter(psy_item %in% c(paste0("entityRelevance_",exc.ent.countarray))) %>% select(concept,value) %>% mutate(class = "Entities") %>% mutate(concept = factor(concept, levels = rev(getConceptList_Entities(lan))))


exc.sr.rel = ds2 %>% filter(psy_item %in% c(paste0("relationshipRelevance_",exc.rel.countarray))) %>% select(concept,value) %>% mutate(class = "Relationships") %>% mutate(concept = factor(concept, levels = rev(getConceptList_Relationships(lan))))

exc.sr.ent.plot = ggplot(exc.sr.ent,aes(y=concept,x = value)) + geom_boxplot(fill = "brown3",color = "black") + xlab("Excess (0-10)") + xlim(0,10) + ylab("Concept")

exc.sr.rel.plot = ggplot(exc.sr.rel,aes(y=concept,x = value)) + geom_boxplot(fill = "darkcyan",color = "black") + xlab("Excess (0-10)") + xlim(0,10) + ylab("Concept")


if (printIMGData) {
  ggsave(plot = arrangeGrob(exc.sr.ent.plot,
               exc.sr.rel.plot,
               nrow=1),
            paste0(paperPath,"img/",lan,"-fig-exc-self.pdf"), 
            width = 350, height = 180, units = "mm")
}

```

## Relationship to self-reported 

```{r eval=TRUE}


excessCorr = ds2 %>% filter(psy_item %in% c(paste0("entityRelevance_",exc.ent.countarray),paste0("relationshipRelevance_",exc.rel.countarray))) %>% 
  inner_join(exc.pp, by = c("participant" = "participant", "conceptID" = "option", "language" = "language")) %>% rename(excess = exc_V_pp)


exc.self.corr.plot = ggplot(excessCorr,aes(x=value, y = excess)) + geom_point() + geom_smooth(method='lm', formula= y~x) + xlab("Self Reported Excess") + ylab("Self Reported Excess") + bigthema

if (printIMGData) {
   ggsave(plot = exc.self.corr.plot, paste0(paperPath,"img/",lan,"-fig-exc-corr.pdf"), 
          width = 350, height = 180, units = "mm")
}

(excessCorr.corr = cor.test(
  excessCorr %>% pull(value),
  excessCorr %>% pull(excess),
  method = "kendall",exact = FALSE,alternative = "less"))
```




# Redundancy and Overlaps {.tabset}

## Observational - Fine

```{r eval=TRUE, fig.width = 7}

OVI.ent = overlaps.per.item(observations = observations %>% filter(class == "entity"),
                  l = lan,
                  getConceptCodeList_Entities(lan,concepts_df),
                  overlapFunc = ov2,
                  threshold = 0.1)

OVI.rel = overlaps.per.item(observations = observations %>% filter(class == "relationship"),
                  l = lan,
                  getConceptCodeList_Relationships(lan,concepts_df),
                  overlapFunc = ov2,
                  threshold = 0.1)


# Tiles -------------
ovi.tile.obs <- grid.arrange(
  blackOvTile(OVI.ent$tile,statistic = mean, "iStar-RL, Entities",huelim = c(0,0.5)),
  blackOvTile(OVI.rel$tile,statistic = mean, "iStar-RL, Relationships",huelim = c(0,0.5))) + 
  theme(plot.margin = unit(c(1,1,1,1),"cm"))

ovi.tile.obs.paper = arrangeGrob(
  blackOvTile(OVI.ent$tile,statistic = mean, "iStar-RL, Entities",huelim = c(0,1)),
  blackOvTile(OVI.rel$tile,statistic = mean, "iStar-RL, Relationships",huelim = c(0,1))
)

if (printIMGData){
  ggsave(plot = ovi.tile.obs.paper,
         paste0(paperPath,"img/",lan,"fig-tiles-obs.pdf"), device = "pdf",
         width = 350, height = 200, units = "mm")
}


# Alternative Visual
ovi.tile.obs.paper.blue = arrangeGrob(
  blueOvTile(OVI.ent$tile,huelim = c(0,1), title = "iStar-RL, Entities"),
  blueOvTile(OVI.rel$tile,huelim = c(0,1), title = "iStar-RL, Relationships")
)


if (printIMGData){
  ggsave(plot = ovi.tile.obs.paper.blue,
         paste0(paperPath,"img/",lan,"fig-tiles-obs-blue.pdf"), device = "pdf",
         width = 350, height = 200, units = "mm")
}
```


## Redundancy
```{R eval=TRUE}
red.tab = rbind(
  redundancy(OVI.ent$stats) %>% mutate(Class = "Entities"),
  redundancy(OVI.rel$stats) %>% mutate(Class = "Relationships")
) %>% relocate(Class,.before = Concept)

kable(red.tab, digits = 2, "simple")

areYouSure = TRUE
if (printTEXData & areYouSure) {
  sink(file = paste0(paperPath,lan,"-red-list.tex"))
  print(xtable(red.tab,
       caption = "Redundancy indices.",
       label = "tab:red"))
  sink(file = NULL)
}
```

## Observational - Coarse

```{r,eval=TRUE, fig.width = 7}

collapse_vec_ent = c(
  actor = "Actor",
  goal = "Goal",
  task = "Task",
  `eff-sat` = "Effect",
  `eff-nonsat` = "Effect",
  `eff-ind` = "Effect",
  `eff-pre` = "Effect",
  qual = "Quality",
  `qual-pre` = "Effect",
  None = "None"
)


collapse_vec_rel = c(
  wants = "wants to",
  and = "is AND-refined to",
  or = "is OR-refined to",
  `eff-link-nondet` = "affects",
  `eff-link-det` = "affects",
  `contr-pos` = "affects",
  `contr-neg` = "affects",
  contr = "affects",
  pre = "precedes",
  None = "None"
)

observations_collapsed_ent = 
  observations %>% filter(class == "entity") %>%
  mutate(option_col = collapse_vec_ent[option]) %>% group_by(participant,item,item_full,language,class,option_col) %>% summarise(response = max(response)) %>% ungroup() %>% rename("option" = option_col)

OVI.ent.collapsed = overlaps.per.item(observations = observations_collapsed_ent,
                  l = lan,
                  unique(collapse_vec_ent[!collapse_vec_ent == 'None']),
                  overlapFunc = ov2,
                  threshold = 0.1)


observations_collapsed_rel = 
  observations %>% filter(class == "relationship") %>%
  mutate(option_col = collapse_vec_rel[option]) %>% group_by(participant,item,item_full,language,class,option_col) %>% summarise(response = max(response)) %>% ungroup() %>% rename("option" = option_col)


OVI.rel.collapsed = overlaps.per.item(observations = observations_collapsed_rel,
                  l = lan,
                  unique(collapse_vec_rel[!collapse_vec_rel == 'None']),
                  overlapFunc = ov2,
                  threshold = 0.1)


# Tiles -------------
ovi.tile.obs.collapsed <- grid.arrange(
  blackOvTile(OVI.ent.collapsed$tile,statistic = mean, "iStar-RL, Entities",huelim = c(0,0.5)),
  blackOvTile(OVI.rel.collapsed$tile,statistic = mean, "iStar-RL, Relationships",huelim = c(0,0.5))) + 
  theme(plot.margin = unit(c(1,1,1,1),"cm"))

ovi.tile.obs.paper.collapsed = arrangeGrob(
  blackOvTile(OVI.ent$tile,statistic = mean, "iStar-RL, Entities",huelim = c(0,1)),
  blackOvTile(OVI.rel$tile,statistic = mean, "iStar-RL, Relationships",huelim = c(0,1))
)

if (printIMGData){
  ggsave(plot = ovi.tile.obs.paper.collapsed,
         paste0(paperPath,"img/",lan,"fig-tiles-obs-collapsed.pdf"), device = "pdf",
         width = 350, height = 200, units = "mm")
}


# Alternative Visual
ovi.tile.obs.paper.blue = arrangeGrob(
  blueOvTile(OVI.ent.collapsed$tile,huelim = c(0,1), title = "iStar-RL, Entities"),
  blueOvTile(OVI.rel.collapsed$tile,huelim = c(0,1), title = "iStar-RL, Relationships")
)


if (printIMGData){
  ggsave(plot = ovi.tile.obs.paper.blue,
         paste0(paperPath,"img/",lan,"fig-tiles-obs-blue-collapsed.pdf"), device = "pdf",
         width = 350, height = 200, units = "mm")
}
```



## Self-reported

```{R eval=TRUE}
self.tile.ents = ds2 %>% 
  filter(str_starts(psy_item,"conceptOverlap_ent")) %>%
  select(concept,value) %>% 
  rename("Pair" = concept) %>% 
  group_by(Pair) %>% summarise(Overlap = mean(value)/10) %>% separate(Pair , c("Concept1","Concept2")," -\\[vs\\]- ") %>%
  mutate(Concept1 = str_extract(Concept1, "^\\S+")) %>%
  mutate(Concept2 = str_extract(Concept2, "^\\S+"))

self.tile.ent = rbind(self.tile.ents, self.tile.ents %>% rename("Concept1" = Concept2, "Concept2" = Concept1)) %>% rename("Obs" = Overlap) %>% 
  mutate(concept1 = factor(Concept1),
         concept2 = factor(Concept2)) 


self.tile.rels = ds2 %>% 
  filter(str_starts(psy_item,"conceptOverlap_rel")) %>%
  select(concept,value) %>% 
  rename("Pair" = concept) %>% 
  group_by(Pair) %>% summarise(Overlap = mean(value)/10) %>% separate(Pair , c("Concept1","Concept2")," -\\[vs\\]- ")  %>%
  mutate(Concept1 = if_else(str_starts(Concept1, "affects"), "affects", Concept1)) %>%
  mutate(Concept2 = if_else(str_starts(Concept2, "affects"), "affects", Concept2)) %>%
  mutate(Concept1 = if_else(str_starts(Concept1, "contributes to"), "contributes to", Concept1)) %>%
  mutate(Concept2 = if_else(str_starts(Concept2, "contributes to"), "contributes to", Concept2))
  

self.tile.rel = rbind(self.tile.rels, self.tile.rels %>% rename("Concept1" = Concept2, "Concept2" = Concept1)) %>% rename("Obs" = Overlap) %>% 
  mutate(concept1 = factor(Concept1),
         concept2 = factor(Concept2)) 


blueOvTile(self.tile.ent, statistic = Obs, title = paste0(lan_long,",  Entities (self-reported)"))
blueOvTile(self.tile.rel, statistic = Obs, title = paste0(lan_long,",  Relationships (self-reported)"))

blackOvTile(self.tile.ent, statistic = Obs, title = paste0(lan_long,",  Entities (self-reported)"))
blackOvTile(self.tile.rel, statistic = Obs, title = paste0(lan_long,",  Relationships (self-reported)"))

ovi.tile.self.paper.blue = arrangeGrob(
        blueOvTile(self.tile.ent, statistic = Obs, title = paste0(lan_long,",  Entities (self-reported)")),
        blueOvTile(self.tile.rel, statistic = Obs, title = paste0(lan_long,",  Relationships (self-reported)"))
)

ovi.tile.self.paper = arrangeGrob(
        blueOvTile(self.tile.ent, statistic = Obs, title = paste0(lan_long,",  Entities (self-reported)")),
        blueOvTile(self.tile.rel, statistic = Obs, title = paste0(lan_long,",  Relationships (self-reported)"))
)




if (printIMGData){
  ggsave(plot = ovi.tile.self.paper.blue,
         paste0(paperPath,"img/",lan,"fig-tiles-self-blue.pdf"), device = "pdf",
         width = 350, height = 350, units = "mm")
  ggsave(plot = ovi.tile.self.paper,
         paste0(paperPath,"img/",lan,"fig-tiles-self.pdf"), device = "pdf",
         width = 350, height = 350, units = "mm")
}


```
